A Horrocks-type theorem for even orthogonal $K_2$

### 2019-09-28 dl-paper.tex
Minor

\subsection{The subgroups $K(\alpha, \beta)$ and their properties} \label{sec:Pa0-Steinberg}
Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df}\label{def:Kab} Denote by $\widetilde{K}(\alpha, \beta)$ the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following five families of elements parametrized by $\xi \in A[X]$, $f\in M[X]$:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate}
Denote by $K(\alpha, \beta)$ the image of $\widetilde{K}(\alpha, \beta)$ under $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X\inv])$. \end{df}

@@

It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap j_+(K(A[X], M[X]))$. The reverse inclusion follows from the just proved decomposition and the fact that for $g\in j_+(K(A[X], M[X]))$ one has $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$ (cf.~\cref{rem:palpha}). \end{proof}

@@

If $\langle \beta, \gamma \rangle$ is $0$ or $1$, then $g$ is a generator of type 2 or 3 for $P_\beta(0)$ in the sense of~\cref{defP0}. Finally, $g = z_\beta(f, X\xi)$ also belongs to $P_\beta(0)$ (this follows e.\,g. from Remarks~\ref{Pstar-char}--\ref{rem:palpha}). \end{proof}

>>>>

\subsection{The subgroups $K(\alpha, \beta)$ and their properties} \label{sec:Pa0-Steinberg}
Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df}\label{def:Kab} Denote by $\widetilde{K}(\alpha, \beta)$ the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parametrized by $\xi \in A[X]$, $f\in M[X]$:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate}
Denote by $K(\alpha, \beta)$ the image of $\widetilde{K}(\alpha, \beta)$ under $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X\inv])$. \end{df}

@@

It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap j_+(K(A[X], M[X]))$. The reverse inclusion follows from the just proved decomposition and the fact that for $g\in j_+(K(A[X], M[X]))$ holds $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$ (cf.~\cref{rem:palpha}). \end{proof}

@@

If $\langle \beta, \gamma \rangle$ is $0$ or $1$, then $g$ is a generator of type 2 or 3 for $P_\beta(0)$ in the sense of~\cref{defP0}. Finally, if $\gamma = \beta$ the element $g = z_\beta(f, X\xi)$ also belongs to $P_\beta(0)$ (this follows e.\,g. from Remarks~\ref{Pstar-char}--\ref{rem:palpha}). \end{proof}
